Combinatorial interpretations of holonomic recurrences

### 2021-08-15 article/main.tex
Fix images

@@

\includeinlinesvg{.19}{images/trees_00/4_base.svg}%
\(\Rightarrow\)
\includeinlinesvg{.19}{images/trees_00/4.svg}%
\includeinlinesvg{.19}{images/trees_00/5.svg}%
\includeinlinesvg{.19}{images/trees_00/6.svg}%
\includeinlinesvg{.19}{images/trees_00/7.svg}%

If we take a look at more examples, we can start seeing some patterns:

\includeinlinesvg{.33}{images/trees_00/2.svg}%
\includeinlinesvg{.33}{images/trees_00/3.svg}%
\includeinlinesvg{.33}{images/trees_00/7.svg}%

\includeinlinesvg{.33}{images/trees_00/4.svg}%
\includeinlinesvg{.33}{images/trees_00/12.svg}%
\includeinlinesvg{.33}{images/trees_00/13.svg}%

\includeinlinesvg{.20}{images/trees_00/0.svg}%
\includeinlinesvg{.20}{images/trees_00/1.svg}%
\includeinlinesvg{.20}{images/trees_00/5.svg}%
\includeinlinesvg{.20}{images/trees_00/6.svg}%
\includeinlinesvg{.20}{images/trees_00/8.svg}%

\includeinlinesvg{.20}{images/trees_00/9.svg}%
\includeinlinesvg{.20}{images/trees_00/10.svg}%
\includeinlinesvg{.20}{images/trees_00/11.svg}%
\includeinlinesvg{.20}{images/trees_00/14.svg}%
\includeinlinesvg{.20}{images/trees_00/15.svg}%

The order may be a bit suggestive. Let's take a look at class \(1\). Section \(1,0\) adds single \(l\) node, section \(1,1\) adds single \(s\) node. It actually suggests how can we can try to generate first and second line of the trees above. The first one is simple. Let's add \(l\) node with pointed right virtual node to each actual node:

@@

\includeinlinesvg{.24}{images/trees_100/0_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/0.svg}%
\includeinlinesvg{.24}{images/trees_100/1_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/1.svg}%

\includeinlinesvg{.24}{images/trees_100/2_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/2.svg}%
\includeinlinesvg{.24}{images/trees_100/3_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/3.svg}%

It addresses all cases from the first line. It introduces incorrect lambda tree though in which \(s\) is parent of \(l\), which can not happen. We will fix it with the section \(2,2\) generating positive trees, which introduces one \(l\) node and one \(s\) by extending the tree with \(2\) nodes where \(s\) is parent of \(l\).

>>>>

\svgpath{images/}

@@

\includeinlinesvg{.19}{trees_00__4_base.svg}%
\(\Rightarrow\)
\includeinlinesvg{.19}{trees_00__4.svg}%
\includeinlinesvg{.19}{trees_00__5.svg}%
\includeinlinesvg{.19}{trees_00__6.svg}%
\includeinlinesvg{.19}{trees_00__7.svg}%

If we take a look at more examples from class \(0\), we can start seeing some patterns:

\includeinlinesvg{.33}{trees_00__2.svg}%
\includeinlinesvg{.33}{trees_00__3.svg}%
\includeinlinesvg{.33}{trees_00__7.svg}%

\includeinlinesvg{.33}{trees_00__4.svg}%
\includeinlinesvg{.33}{trees_00__12.svg}%
\includeinlinesvg{.33}{trees_00__13.svg}%

\includeinlinesvg{.20}{trees_00__0.svg}%
\includeinlinesvg{.20}{trees_00__1.svg}%
\includeinlinesvg{.20}{trees_00__5.svg}%
\includeinlinesvg{.20}{trees_00__6.svg}%
\includeinlinesvg{.20}{trees_00__8.svg}%

\includeinlinesvg{.20}{trees_00__9.svg}%
\includeinlinesvg{.20}{trees_00__10.svg}%
\includeinlinesvg{.20}{trees_00__11.svg}%
\includeinlinesvg{.20}{trees_00__14.svg}%
\includeinlinesvg{.20}{trees_00__15.svg}%

The order may be a bit suggestive. Section \(1,0\) adds single \(l\) node, whereas section \(1,1\) adds single \(s\) node. It actually suggests how can we can try to generate first and second line of the trees above. The first one is simple. Let's add \(l\) node with pointed right virtual node to each actual node:

@@

\includeinlinesvg{.24}{trees_100__0_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__0.svg}%
\includeinlinesvg{.24}{trees_100__1_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__1.svg}%

\includeinlinesvg{.24}{trees_100__2_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__2.svg}%
\includeinlinesvg{.24}{trees_100__3_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__3.svg}%

It addresses all cases from the first line, but also introduces incorrect lambda tree in which \(s\) is parent of \(l\), which can not happen. We will fix it with the section \(2,2\) generating positive trees, which introduces one \(l\) node and one \(s\) by extending the tree with \(2\) nodes where \(s\) is parent of \(l\).
